Standalone Tactics using OpenTheory

### 2012-05-12 paper.tex
Added a reference to PROSPER
add newlines between institutions and emails
in accordance with Springer guidelines
Minor changes and a paragraph on the PROSPER related work

\institute{University of Cambridge, \email{Ramana.Kumar@cl.cam.ac.uk}\and Galois, Inc., \email{joe@gilith.com}}

@@

In addition to the development effort, the costs of maintenance can also be multiplied over different systems, and improvements in functionality can become restricted to a single system unnecessarily.
For instance, the Metis first order logic prover~\cite{hurd2003d} is integrated in multiple systems in the HOL family, but the HOL4 version is very old compared to the latest version in Isabelle/HOL.
Slind's TFL package for defining recursive functions~\cite{slindphd}, originally implemented for both Isabelle/HOL and HOL4, was superseded in Isabelle/HOL by Krauss's function definition package~\cite{DBLP:journals/jar/Krauss10}.
The improvements of Krauss's method over TFL ought to be applicable to other HOL-based provers, but a direct reimplementation would require substantial effort.

@@

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements of the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} Ability to read and write \OpenTheory article files.

@@

>>>>

\institute{ University of Cambridge\\\email{Ramana.Kumar@cl.cam.ac.uk}\\\and Galois, Inc.\\\email{joe@gilith.com}}

@@

In addition to the development effort, the cost of maintenance can also be multiplied over different systems, and improvements in functionality can become restricted to a single system unnecessarily.
For instance, the Metis first order logic prover~\cite{hurd2003d} is integrated in multiple systems in the HOL family, but the HOL4 version is very old compared to the latest version in Isabelle/HOL.
Slind's TFL package for defining recursive functions~\cite{slindphd}, originally implemented for both Isabelle/HOL and HOL4, was superseded in Isabelle/HOL by Krauss's function definition package~\cite{DBLP:journals/jar/Krauss10}.
The improvements of Krauss's method over TFL ought to be applicable to other HOL-based provers, but a direct reimplementation would require substantial effort.

@@

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements for the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} Ability to read and write \OpenTheory article files.

@@

The PROSPER project~\cite{dennis2000} pioneered the technique of sending goals over the internet to a remote solver, and packaging such procedures as tactics in the HOL4 theorem prover. The standalone tactics described in this paper further systematize this by using \OpenTheory as a standard language and ontology to make it easier for interactive theorem provers and remote solvers to communicate.
